Simply Grasping Simple Shapes:\\ Commanding a Humanoid Hand with a Shape-Based Synergy

### 2017-10-16 draft_springer_2.tex
so, for some reason, it says I deleted everything and re-wrote it. I didn't I fixed some wordings, reworked some ares. I put the sections back into discussion and flipped them around. I think its more clear. I consolodated results down to 1 section.

\begin{abstract}
Despite rapid advancements in dexterity and mechanical design, the utility of humanoid robots in an uncontrolled laboratory setting is limited in part due to the complexity involved in programming robots to grasp common objects. There exists a need for an efficient method to command high degree-of-freedom (DoF) dexterous manipulators for a range of objects such that explicit models are not needed for every interaction. The authors propose a method incorporating the neuroscience concept of postural synergies to decrease the commanded DoFs to match intuitive measurements of an object, which we term geometrical synergies.  The approach of this paper is similar to that of Ciocarlie et al. \cite{ciocarlieallen}, however, rather than testing the postural synergies that come from the principle components of a human grasps, the authors design a grasping synergy based on the object that is meant to be grasped.  For this paper, the synergy was designed to grasp cylinder-shaped objects. Using the SynGrasp toolbox, a model of Robonaut 2`s twelve-DoF hand was created to perform contact analysis around a small set of cylinders defined by a single variable, diameter. Experiments were performed on the robot to validate and update the synergy-based models.  Successful manipulation of a large range of cylindrical objects, not previously introduced to the robot, was demonstrated in a proof-of-concept experiment. This synergy-based grasp planning method can be applied to any humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs, to grasp commonly shaped objects, vastly multiplying the library of objects the robot can manipulate.
\keywords{Manipulation, grasp, synergy, humanoid, dexterous, hand}
\end{abstract}

@@

Humanoid robots provide the capability to operate in the same space, using the same tools that a human can. The future of these robots can clearly be seen with efforts for robots to go into disaster areas unsafe for humans \cite{fukushima_robots} or help humans do menial tasks. Perhaps the most fundamental capability necessary to accomplish these human tasks is the ability to manipulate the same objects that humans can. For this challenge, many designers have created hands capable of nearly all of the DoFs as the human hand \cite{r2_hand}, \cite{DRL}, \cite{hrp3}, \cite{softhand}. However, while the hands are able to form many of the same grips and poses as a human hand, the control of these hands in an intuitive, and simple way has yet to be demonstrated. Until the community can quickly and effectively control these high DoF humanoid hands, robots will still need to be highly specialized for individual tasks. \par
Research shows that humans control their hands not with individual joint position commands, as dexterous robot hands are typically controlled, but instead by a single signal that actuates multiple muscle groups. These groups combine to create the plethora of hand motions humans can form \cite{Santello} \cite{neuro}. This approach gives a method for decreasing the commanded DoF of the hand system to a more manageable number, and is referred to as ``synergies". These synergy schemes represen the principle components of various grasps of the human hand. These components can be difficult to intuitively combine into useful hand motions, shifting the complexity problem from DoF, to nonintuitive combinations of synergies. \par
The contribution of this paper is a methodology to decrease the commanded DoF from twelve to one for the Robonaut 2 (R2) hand to manipulate simple cylindrical shapes. This methodology replaces all unique cylindrical type models with a single model to allow simple manipulation of common objects. In addition, the single commanded DoF is based on a simple measurement of the object to allow intuitive control. This enables the robot to successfully manipulate any cylindrical object found in its environment with the single model.

@@

\subsection{Hand Synergies}
	Dexterous manipulation in robots has developed from a simple parallel gripper towards the complexity of the human hand in the past decades. These devices are high DoF systemsthat allow robots to manipulate objects in similar ways to a human. However, as this problem has been studied further, the construction of robotic hands with similar DoFs as the human hand has become common place, but the control is anything but intuitive. The computational costs to calculate the correct closing position around a given object as perceived by a robotic vision system is $O(2^N)$
 where N represents the number of DoFs, with each DoF controlled individually. Researchers have focused on analyzing the way that humans control our own hands with hopes of extending that same control scheme to a robotic hand, as in the seminal work on postural synergies of human grasping \cite{Santello}.

@@

NASA is actively developing humanoid robotics to work in the same environment as astronauts. To this end, Robonaut 2 is a humanoid robot with two 7 DoF arms (including the wrist), a 3 DoF neck, 1 DoF waist, two 12 DoF hands, and two 7 DoF legs. This robot is currently on board the International Space Station. The design goal of this robot is to assist astronauts with repetitive tasks on the International Space Station like monitoring airflow, cleaning handrails, and unpacking resupply vehicles \cite{r2_diftler}. Currently, NASA is actively developing technologies to allow this robot to behave with more autonomy. This is necessary to allow supervised control over long time delays as missions progress farther and farther from Earth.

@@

\subsection{Current R2 Grasping Process}

R2's command structure centers around the concept of multi-loop control with a progressive series of loops \cite{r2_control}. The lowest level of control is a current loop, wrapped by a velocity loop, wrapped by a torque loop, and finally wrapped by a position loop that the user is dictating. However, the R2 finger actuators are not series elastic and have no direct torque measurement. Therefore, the torque loop is removed in the multi-loop control model and current limiting is placed at the lowest level to protect the finger tendons. This loop structure eliminates the capability to do direct torque control of the fingers to close around an object. This dictates the need for a position control scheme to command the hand to manipulate objects.

@@

Due to this position control scheme, the original grasp process used by R2 was based on the Cutkosky Grasp Taxonomy \cite{Cutkosky}. This series of 24 position defined grasps composed the main method of manipulating an object in conjunction with the Affordance Template Framework \cite{affordance_templates} similar to systems used on other humanoid robots \cite{DRC_Yanco}, \cite{IHMC}. However, each of these templates, an example of which is shown in Fig \ref{at_example}, is unique to the object using one of the Cutcosky grasps. If a new grasp is needed, it must be created, tested and verified. If a new object that is slightly different than a current known object is encountered, a new Affordance Template and grasp must be created and tested.

This creation of templates and gasp positoins can be time consuming and very application specific and is intractable at a large scale for robots in practice. In addition, the current proposed methods of using the synergies based on the PCA of the human hand are equally non-intuitve to program in a position based scheme. Therefore, a commanding structure to determine hand position based on simple properties of the object is proposed. Specifically for this work, the authors propose a geometric synergy based on cylindrical type objects. The finger position can be commanded based on the single DoF dictated by the diamter of the object. This would allow a flashlight, a coffee cup, a screwdrirver, and any other cylinder to be manipulated using the same cylindrical template based solely on the objects diameter.

\section{Methods}

@@

% take this section from 3 paragraphs down to 3 sentences. We basically say all of this somewhere else. 
A synergistic command structure can be mathematically defined in (2).
$$
q = S\sigma  \eqno{(2)}
$$

where $q$ is the vector of joint angles of dimensions [$N*1$],  $N$ is the number of synergies, $S$ is the synergy matrix of dimensions [$N*M$],  $M$ is the number of possible synergies that can be activated and $\sigma$ is the [$M *1$] synergy activation vector which determines which synergy or combination thereof is turned on.  The basis of synergies is that the generic joint displacement, $q$, can be represented as a function of fewer elements than the number of DoFs of the system.  $S$ is a vector of weights that determines the amount of motion for an individual joint resulting from a single input.  In neuroscience, these $S$ matrices are determined by mapping the grasps of various shapes and isolating the movements of individual joints.  The covariances of the various joint angles are analyzed and combined using machine learning to identify when joints are commonly moved in unison, a weighing scalar based on the relative magnitude of motion.  Rather than identifying and isolating synergies from existing behavior as is done in neuroscience, the authors aim to design a synergy by providing an $S$ matrix such that the finger joints move in unison to produce a cylinder grasp.  For this reason, the synergy matrix is designed based on grasp shapes for various sized cylinders.

@@

\subsection{Model Refinement and Synergy Development}
The models were validated by commanding R2's hand to close around a cylindrical piece of aluminum exactly equal to our modeled diameter using the values dictated by SynGrasp. The grasps were tested and refined using the previously mentioned test method and the model discrepancies were accounted for. These discrepancies are discussed in detail in Section \ref{discussion}. Once the final values from testing were established, the results from each cylinder diameter for each finger were plotted and a polynomial fit to the data was carried out. The fits were calculated so that the maximum error for each data point was 4 degrees.   The maximum order used was three, however, many of the joints required lower orders. The resulting relationships were relatively simple which intuitively makes sense. As the object gets larger, the hand opens more. The thumb is the only digit which changed orientations substantially as the diameters got larger as it has more DoF to move into a suitable position. The graph of the thumb joint angle fits are shown in Fig. \ref{thumb_fits}.

@@

After model validation on the robot and subsequent adjustments, the robot was able to manipulate fifteen objects in the experiment using the single synergy commanding structure. In addition, five non-cylindrical objects were tested that demonstrated the applicability of this synergy to more than pure cylinders as well as the cases in which this method is not applicable.

\subsection{Synergy Testing}

Twenty common objects found in a laboratory setting were tested to validate the effectiveness of the curve fits creating the synergy. The list of these objects as well as their success can be viewed in Fig. \ref{objects}.  Of the 20 objects manipulated, 17 were manipulated with no issues, 1 slipped in the grip, and 2 were dropped outright.

\section{Discussion}
\label{discussion}

Of the objects selected and tested, 15 could be considered pure cylinders. Of these cylinders, the only one not successfully manipulated at all was the large flashlight. This object slid out of the robot's grasp as it was manipulated. A qualitative evaluation of the grasp suggested the fingers were in an appropriate position. The flashlight was the heaviest object manipulated by the robot (1 kg) and the friction that the robot could apply through the normal force and the glove material was inadequate to manipulate it. The authors believe this is not achievable by the robot regardless of the method of grasp determination. In addition, the robot did not maintain a firm grasp on the hammer. The hammer shank diameter is at the small end of the range that the robot is able to grasp even with a full hand close position due the kinematics of the hand joints and the friction of the glove. The hammer slid in the grasp, but was not dropped. In practice, R2 would be able to manipulate this object to a new location. R2 maintained solid control of the object for all the other cylinders.

Four prismatic objects were tested to understand the model applicability outside of a pure cylinder. The robot succeeded in manipulating each of these four objects. This suggests that this grasp abstracts to more than cylinders, instead, it could be considered a power grasp synergy based on the Cutkosky Grasps, further generalizing the theory.

@@

%\subsection{SynGrasp Model Validation}

The SynGrasp model provided a very useful method to determine a starting point for grasp refinement. The SynGrasp model remains an idealized model of the robot hand. Many aspects could not be accurately modeled and had to be adjusted through the model validation process, as discussed below. Future additions to the software to allow more realistic actuation could include friction models and more control over the geometry of the hand, as R2's palm is larger than the model allowed. Going forward, SynGrasp is useful for other synergy types such as pinch grasp which has contact forces only in the fingers and does not require use of the palm.

In addition, the 4 DoF thumb has many possible locations in which it could contact the cylinder in SynGrasp, and due to the redundant DoF, the thumb location choice performed poorly for larger objects near 7.62 cm diameter. Primarily, the thumb would roll too close to the palm, giving a point contact on the thumb pad for larger diameters rather than a wrap around the cylinder. The thumb position was adjusted via testing. The index and middle finger values still proved valid.

@@

%\subsection{Applicability and Future Work}

%The approach demonstrated in this work shows a useful method of grasping objects commonly manipulated through a power grasp. There is a simple logical step to then apply these methods to determine the synergies for other types of grasp such as a pinch grasp or ball grasp, and effectively change the Cutkosky grasps from single shapes, to sets of relationships. However, to truly do human type manipulation, the individually commanded DoF must remain as shown with the Dewalt drill manipulation. This type of manipulation could be captured in this framework via an additional synergy focused on the position of the index finger. These simple additions could allow individual finger actions that are still intuitive to program to be added to the overall hand motions that have been demonstrated to work.

>>>>

\begin{abstract}
Despite rapid advancements in dexterity and mechanical design, the utility of humanoid robots in an uncontrolled laboratory setting is limited in part due to the complexity involved in programming robots to grasp common objects. There exists a need for an efficient method to command high degree-of-freedom (DoF) dexterous manipulators for a range of objects such that explicit models are not needed for every interaction. The authors propose a method incorporating the neuroscience concept of postural synergies to decrease the commanded DoFs to match intuitive measurements of an object, which we term geometrical synergies.  The approach of this paper is similar to that of Ciocarlie et al. \cite{ciocarlieallen}, however, rather than testing the postural synergies that come from the principle components of a human grasps, the authors design a grasping synergy based on the object that is meant to be grasped.  For this paper, the synergy was designed to grasp cylinder-shaped objects. Using the SynGrasp toolbox, a model of Robonaut 2`s twelve-DoF hand was created to perform contact analysis around a small set of cylinders defined by a single variable, diameter. Experiments were performed on the robot to validate and update the synergy-based models.  Successful manipulation of a large range of cylindrical objects, not previously introduced to the robot, was demonstrated in a proof-of-concept experiment. This synergy-based grasp planning method can be applied to any humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs, to grasp commonly shaped objects, vastly multiplying the library of objects the robot can manipulate.
\keywords{Manipulation, Grasp, Synergy, Humanoid, Dexterous Hand}
\end{abstract}

@@

Humanoid robots provide the capability to operate in the same space, using the same tools that a human can. The future of these robots can clearly be seen with efforts for robots to go into disaster areas unsafe for humans \cite{fukushima_robots} or help humans do menial tasks. Perhaps the most fundamental capability necessary to accomplish these human tasks is the ability to manipulate the same objects that humans can. For this challenge, many designers have created hands capable of nearly all of the DoFs as the human hand \cite{r2_hand}, \cite{DRL}, \cite{hrp3}, \cite{softhand}. However, while the hands are able to form many of the same grips and poses as a human hand, the control of these hands in an intuitive and simple way has yet to be demonstrated. Until the community can quickly and effectively control these high DoF humanoid hands, robots will still need to be highly specialized for individual tasks. \par
Research shows that humans control their hands not with individual joint position commands, as dexterous robot hands are typically controlled, but instead by a single signal that actuates multiple muscle groups. These groups combine to create the plethora of hand motions humans can form \cite{Santello} \cite{neuro}. This approach gives a method for decreasing the commanded DoF of the hand system to a more manageable number, and is referred to as ``synergies". These synergy schemes represent the principle components of various grasps of the human hand. These components can be difficult to intuitively combine into useful hand motions, shifting the complexity problem from DoF, to nonintuitive combinations of synergies. \par
The contribution of this paper is a methodology to decrease the commanded DoF from twelve to one for the Robonaut 2 (R2) hand to manipulate simple cylindrical shapes. This methodology replaces all unique cylindrical type models with a single model to allow simple manipulation of common objects. In addition, the single commanded DoF is based on a simple measurement of the object to allow intuitive control. This enables the robot to successfully manipulate any cylindrical object found in its environment with the single model.

@@

\subsection{Hand Synergies}
	Dexterous manipulation in robots has developed from a simple parallel gripper towards the complexity of the human hand in the past decades. These devices are high DoF systems that allow robots to manipulate objects in similar ways to a human. However, as this problem has been studied further, the construction of robotic hands with similar DoFs as the human hand has become common place, but the control is anything but intuitive. The computational costs to calculate the correct closing position around a given object as perceived by a robotic vision system is $O(2^N)$
 where N represents the number of DoFs, with each DoF controlled individually. Researchers have focused on analyzing the way that humans control our own hands with hopes of extending that same control scheme to a robotic hand, as in the seminal work on postural synergies of human grasping \cite{Santello}.

@@

NASA is actively developing humanoid robotics to work in the same environment as astronauts. To this end, Robonaut 2 is a humanoid robot with two 7 DoF arms (including the wrist), a 3 DoF neck, 1 DoF waist, two 12 DoF hands, and two 7 DoF legs. R2 is currently on board the International Space Station. The design goal of this robot is to assist astronauts with repetitive tasks on the International Space Station like monitoring airflow, cleaning handrails, and unpacking resupply vehicles \cite{r2_diftler}. Currently, NASA is actively developing technologies to allow this robot to behave with more autonomy. This is necessary to allow supervised control over long time delays as missions progress farther and farther from Earth.

@@

\subsection{Current R2 Grasping Process}
REWRITTEN SECTION 
R2's command structure centers around the concept of multi-loop control with a progressive series of loops \cite{r2_control}. The lowest level of control is a current loop, wrapped by a velocity loop, wrapped by a torque loop, and finally wrapped by a position loop that the user is dictating. However, the R2 finger actuators are not series elastic and have no direct torque measurement. Therefore, the torque loop is removed in the multi-loop control model and current limiting is placed at the lowest level to protect the finger tendons. This loop structure eliminates the capability to do direct torque control of the fingers to close around an object, thus dictating the need for a position control scheme to command the hand to manipulate objects.

@@

Due to this position control scheme, the original grasp process used by R2 was based on the Cutkosky Grasp Taxonomy \cite{Cutkosky}. This series of 24 position defined grasps composed the main method of grasping an object. For full manipulation, the CutKosky grasps are used in conjunction with the Affordance Template Framework \cite{affordance_templates}. This implementation is similar to systems used on other humanoid robots \cite{DRC_Yanco}, \cite{IHMC}. However, each of these templates is unique to the object using one of the Cutcosky grasps. An example Affordance Template is shown in Fig \ref{at_example}. If a new grasp is needed, it must be created, tested and verified. If a new object that is slightly different than a current known object is encountered, a new Affordance Template and grasp must be created and tested.

This creation of templates and gasp positions can be time consuming and very application specific and is intractable at a large scale for robots in practice. In addition, the current proposed methods of using the synergies based on the PCA of the human hand are equally non-intuitive to program in a position based scheme. Therefore, a commanding structure to determine hand position based on simple properties of the object is proposed. Specifically for this work, the authors propose a geometric synergy based on cylindrical type objects. The finger position can be commanded based on the single DoF dictated by the diameter of the object. This would allow a flash light, a coffee cup, a screwdriver, and any other cylinder to be manipulated using the same cylindrical template based solely on the objects diameter. 
END REWRITTEN SECTION
\section{Methods}

@@

% take this section from 3 paragraphs down to 3 sentences. We basically say all of this somewhere else. 
A synergistic command structure can be mathematically defined in (1).
$$
q = S\sigma  \eqno{(1)}
$$
where $q$ is the vector of joint angles of dimensions [$N \times 1$],  $N$ is the number of synergies, $S$ is the synergy matrix of dimensions [$N \times M$],  $M$ is the number of possible synergies that can be activated and $\sigma$ is the [$M \times 1$] synergy activation vector which determines which synergy or combination thereof is turned on.  The basis of synergies is that the generic joint displacement, $q$, can be represented as a function of fewer elements than the number of DoFs of the system.  $S$ is a vector of weights that determines the amount of motion for an individual joint resulting from a single input.  In neuroscience, these $S$ matrices are determined by mapping the grasps of various shapes and isolating the movements of individual joints.  The covariances of the various joint angles are analyzed and combined using machine learning to identify when joints are commonly moved in unison, a weighting scalar based on the relative magnitude of motion.  Rather than identifying and isolating synergies from existing behaviour as is done in neuroscience, the authors aim to design a synergy by providing an $S$ matrix such that the finger joints move in unison to produce a cylinder grasp.  For this reason, the synergy matrix is designed based on grasp shapes for various sized cylinders.

@@

\subsection{Model Refinement and Synergy Development}
The models were validated by commanding R2's hand to close around a cylindrical piece of aluminum exactly equal to our modeled diameter using the values dictated by SynGrasp. The grasps were tested and refined using the previously mentioned test method and the model discrepancies were accounted for. These discrepancies are discussed in detail in Section \ref{discussion}. Once the final values from testing were established, the results from each cylinder diameter for each finger were plotted and a polynomial fit to the data was carried out. The fits were calculated so that the maximum error for each data point was 4 degrees.   The maximum order used was three, however, many of the joints required lower orders. The resulting relationships were relatively simple which intuitively makes sense, as the object gets larger, the hand opens more. The thumb is the only digit which changed orientations substantially as the diameters got larger as it has more DoF to move into a suitable position. The graph of the thumb joint angle fits are shown in Fig. \ref{thumb_fits}.

@@

REWRITTEN
After model validation on the robot and subsequent adjustments, the robot was able to manipulate 13 of 15 cylindrical objects in the experiment using the single synergy commanding structure. In addition, five non-cylindrical objects were tested, four of which were nearly square rectangular prisms, and one drill. All four rectangular prism objects were successfully grasped which demonstrated the applicability of this synergy to more than pure cylinders. The drill was not successfully grasped showing an example of the case where this method is not applicable.  The list of these objects as well as their success can be viewed in Fig. \ref{objects}. Of the 20 objects manipulated, 17 were manipulated with no issues, 1 slipped in the grip, and 2 were dropped outright. 
REWRITTEN

\paragraph{}
\section{Discussion}
\label{discussion}

\subsection{SynGrasp Model Validation}

Before the final testing and validation of the system, but SynGrasp model had to be validated. The SynGrasp model provided a very useful method to determine a starting point for grasp refinement, however, the SynGrasp model remains an idealized model of the robot hand. Many aspects could not be accurately modelled and had to be adjusted through the model validation process, as discussed below. Future additions to the software to allow more realistic actuation could include friction models and more control over the geometry of the hand, as R2's palm is larger than the model allowed. Going forward, SynGrasp is useful for other synergy types such as pinch grasp which has contact forces only in the fingers and does not require use of the palm.

In addition, due to a redundant DoF, the 4 DoF thumb has many possible locations in which it could contact the cylinder in SynGrasp which caused the thumb location choice to perform poorly for larger objects near 7.62 cm diameter. Primarily, the thumb would roll too close to the palm, giving a point contact on the thumb pad for larger diameters rather than a wrap around the cylinder. The thumb position was adjusted via testing. The index and middle finger generated by SynGrasp were able to be used with no modifications, demonstrating the usefulness of the initial model in testing and validation.

\subsection{Grasp Success Discussion}
Once the model was validated, the final testing of the method could be performed. Of the objects selected and tested, 15 could be considered pure cylinders. Of these cylinders, the only one not successfully manipulated at all was the large flashlight. This object slid out of the robot's grasp as it was manipulated. A qualitative evaluation of the grasp suggested the fingers were in an appropriate position. The flashlight was the heaviest object manipulated by the robot (1 kg) and the friction that the robot could apply through the normal force and the glove material was inadequate to manipulate it. The authors believe this is not achievable by the robot regardless of the method of grasp determination. In addition, the robot did not maintain a firm grasp on the hammer. The hammer shank diameter is at the small end of the range that the robot is able to grasp even with a full hand close position due the kinematics of the hand joints and the friction of the glove. The hammer slid in the grasp, but was not dropped. In practice, R2 would be able to manipulate this object to a new location. R2 maintained solid control of the object for all the other cylinders.

Four prismatic objects were tested to understand the model applicability outside of a pure cylinder. The robot succeeded in manipulating each of these four objects. This suggests that this grasp abstracts to more than cylinders, instead, it could be considered a power grasp synergy, further generalizing the theory.

@@

@@

\subsection{Applicability and Future Work}
RE-ADDED
The approach demonstrated in this work shows a useful method of grasping objects commonly manipulated through a power grasp. There is a simple logical step to then apply these methods to determine the synergies for other types of grasp such as a pinch grasp or ball grasp, and effectively change the Cutkosky grasps from single shapes, to sets of relationships. However, to truly do human type manipulation, the individually commanded DoF must remain as shown with the Dewalt drill manipulation. This type of manipulation could be captured in this framework via an additional synergy focused on the position of the index finger. These simple additions could allow individual finger actions that are still intuitive to program to be added to the overall hand motions that have been demonstrated to work. 
RE-ADDED
